---
title: "timsBasicVingette"
author: "Timothy M Pierpont"
date: "11/15/2021"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r intro, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This vignette is for the package timsBasicHeatmap

While anyone is free to use this, the code is barely begun to be packaged, so it may or may not be useful for you... This package is more of a test package for the author, Tim.

It uses two identically sized matricies to make a heatmap of values (0-1) and overlay pvalues (1 line for p<0.05, 2 lines for p<0.005). The only input are these two matricies using the function _timsBasicHeatmap_

Column and row names of the first matrix are used to populate the heatmap.

Currently, no other options exist, just passing those two matricies.


```{r cars}
summary(cars)
```

## A quick example

values <- matrix(rnorm(18),nrow=3) #Generates values matrix with random numbers
colnames(values) <- c("CD4","CD8","CD8 Memory","CD8 Naive","Bread","Toast") #Names phenotypes
rownames(values) <- c("Controls","Veh Control","Experimental") #Names groups
pvalues <- abs(matrix(rnorm(18),nrow=3))/5 #Generates pvalues matrix with random numbers that are low and above zero

#these lines simply adjust the numbers in the matricies to look more like you'd expect, they're not necassary for the example
values[1:2,] <- abs(rnorm(6)/3)
pvalues[1,] <- 1
pvalues[2,] <- abs(rnorm(6))
pvalues[3,] <- abs(rnorm(6)/100)



library("timsBasicHeatmap") #Loads the library
timsBasicHeatmap(values,pvalues) #Runs the heatmap with those two matrices
